CF-SuGAR Power Calculations

### 2025-03-20 Christine Chan/CF-SuGAR/power_calculations.qmd
update NIH power calculations

```{r}
exp(lorenz_1hr$coefficients["Baseline_1hr_glucose"] * 0.5)
exp(lorenz_1hr$coefficients["Baseline_1hr_glucose"])
exp(lorenz_1hr$coefficients["Baseline_1hr_glucose"] * 2)
```

>>>>

```{r}
exp(lorenz_1hr$coefficients["Baseline_1hr_glucose"]) * 0.5
exp(lorenz_1hr$coefficients["Baseline_1hr_glucose"])
exp(lorenz_1hr$coefficients["Baseline_1hr_glucose"]) * 2
```
